### 2023-10-28 design/main.tex
Forgot to rename the folders in the mains...
Bunch of changes, added design gru
Bunch of changes, to gru notably
Changed intro design

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|}
    \hline
    \rowcolor{gray}
    Real value & Voltage \\
    \hline
    $0$ & $0.9V$ \\
    \hline
    $1$ & $1.0V$ \\
    \hline
    $x$ & $\frac{x}{10}+V_{cm}$\\
    \hline
    $(V-0.9)\cdot 10$ & $V$\\
    \hline
  \end{tabular}
  \caption{Real/Voltage Conversion Table.}
  \label{tab:valConv}
\end{table}

@@

\input{3.Design/activation.tex}
\input{3.Design/memcell.tex}
\input{3.Design/crossbar.tex}
\input{3.Design/inverter.tex}
\input{3.Design/models.tex}
\input{3.Design/lstm.tex}
\input{3.Design/genwei.tex}
\input{3.Design/netlist.tex}
\input{3.Design/wei2res.tex}
\input{3.Design/dataset.tex}
\input{3.Design/run.tex}
\cleardoublepage

>>>>

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|}
    \hline
    \rowcolor{gray}
    Real value & Voltage \\
    \hline
    $0$ & $0.9V$ \\
    \hline
    $1$ & $1.0V$ \\
    \hline
    $x$ & $V(x)=\frac{x}{10}+V_{cm}$\\
    \hline
    $real(v)=(v-0.9)\cdot 10$ & $v$\\
    \hline
  \end{tabular}
  \caption{Real/Voltage Conversion Table.}
  \label{tab:valConv}
\end{table}

@@

In order to create a fully functional \ac{LSTM} or \ac{GRU} circuit, there are a few components that are required.

An analog activation function circuit to have an analog equivalent to the activation function necessary to the good behavior of \acp{LSTM} and \acp{GRU}.

A memory cell to allow to store the analog value from one time step to the next.

A circuit for the crossbar array, to have a more general circuit that can easily be adapted.

Other, less significant, components required for the circuits to work.

\input{design/activation.tex}
\input{design/memcell.tex}
\input{design/crossbar.tex}
\input{design/inverter.tex}
\input{design/models.tex}
\input{design/lstm.tex}
\input{design/gru.tex}
\input{design/genwei.tex}
\input{design/netlist.tex}
\input{design/wei2res.tex}
\input{design/dataset.tex}
\input{design/run.tex}
\cleardoublepage
